Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 table_fpp.tex
new FPP calculations

$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $7.4\times10^{-4}$ & $1.0\times10^{-4}$ & $0.22$ & $8.4\times10^{-4}$ & Planet \\
 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.011$  & \color{red}  $0.989$  & \color{red}  $0.22$  & \color{red}  $1.000$  & \color{red}  FP\\
$201295312$ & $1$ & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.15$ & $1.1\times10^{-4}$ & Planet \\
$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $5.9\times10^{-4}$ & $0.17$ & $4.6\times10^{-3}$ & Planet \\
$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $7.7\times10^{-4}$ & $< 10^{-4}$ & $0.17$ & $7.7\times10^{-4}$ & Planet \\
$201367065$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.18$ & $1.3\times10^{-3}$ & Planet \\
$201367065$ & $2$ & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
$201384232$ & $1$ & $0.44$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.21$ & $2.3\times10^{-4}$ & Planet \\
$201393098$ & $1$ & $0.52$ &  - & $< 10^{-4}$ & $2.6\times10^{-3}$ & $0.022$ & $0.17$ & $0.025$ & Candidate \\
$201403446$ & $1$ & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $9.8\times10^{-4}$ & $0.13$ & $10.0\times10^{-4}$ & Planet \\
$201445392$ & $1$ & $0.26$ &  - & $< 10^{-4}$ & $1.8\times10^{-3}$ & $0.049$ & $0.22$ & $0.051$ & Candidate \\
$201445392$ & $2$ & $0.18$ &  - & $< 10^{-4}$ & $0.034$ & $0.055$ & $0.18$ & $0.089$ & Candidate \\
$201465501$ & $1$ & $0.68$ &  - & $< 10^{-4}$ & $0.021$ & $3.0\times10^{-3}$ & $0.14$ & $0.025$ & Candidate \\
 \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $0.020$  & \color{red}  $0.966$  & \color{red}  $0.18$  & \color{red}  $0.986$  & \color{red}  FP\\
$201505350$ & $2$ & $0.70$ &  - & $< 10^{-4}$ & $3.0\times10^{-4}$ & $1.2\times10^{-4}$ & $0.07$ & $4.2\times10^{-4}$ & Planet \\
$201546283$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet \\
$201549860$ & $1$ & $0.18$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $6.5\times10^{-4}$ & $0.20$ & $2.4\times10^{-3}$ & Planet \\
$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $5.8\times10^{-4}$ & $3.7\times10^{-4}$ & $0.20$ & $9.5\times10^{-4}$ & Planet \\
 \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}   -  & \color{red}  $2.7\times10^{-3}$  & \color{red}  $0.027$  & \color{red}  $0.926$  & \color{red}  $0.07$  & \color{red}  $0.956$  & \color{red}  FP\\
$201569483$ & $1$ & $2.06$ &  - & $0.468$ & $< 10^{-4}$ & $0.092$ & $0.01$ & $0.560$ & Candidate \\
$201577035$ & $1$ & $0.14$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $1.0\times10^{-4}$ & $0.20$ & $1.1\times10^{-4}$ & Planet \\
$201596316$ & $1$ & $0.45$ &  - & $< 10^{-4}$ & $1.3\times10^{-3}$ & $2.1\times10^{-3}$ & $0.17$ & $3.4\times10^{-3}$ & Planet \\
$201613023$ & $1$ & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.15$ & $< 10^{-4}$ & Planet \\
$201617985$ & $1$ & $0.27$ &  - & $< 10^{-4}$ & $0.016$ & $1.7\times10^{-3}$ & $0.16$ & $0.018$ & Candidate \\
$201629650$ & $1$ & $0.43$ &  - & $< 10^{-4}$ & $6.3\times10^{-4}$ & $1.1\times10^{-3}$ & $0.17$ & $1.7\times10^{-3}$ & Planet \\
$201635569$ & $1$ & $0.79$ &  - & $< 10^{-4}$ & $7.5\times10^{-3}$ & $0.069$ & $0.09$ & $0.076$ & Candidate \\
 \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.819$  & \color{red}  $2.2\times10^{-4}$  & \color{red}  $0.119$  & \color{red}  $0.01$  & \color{red}  $0.938$  & \color{red}  FP\\
$201702477$ & $1$ & $0.70$ &  - & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.277$ & $0.06$ & $0.281$ & Candidate \\
$201736247$ & $1$ & $0.42$ &  - & $< 10^{-4}$ & $1.9\times10^{-4}$ & $8.5\times10^{-4}$ & $0.22$ & $1.0\times10^{-3}$ & Planet \\
$201754305$ & $1$ & $0.65$ &  - & $< 10^{-4}$ & $1.9\times10^{-3}$ & $1.5\times10^{-3}$ & $0.18$ & $3.4\times10^{-3}$ & Planet \\
$201754305$ & $2$ & $0.38$ &  - & $< 10^{-4}$ & $1.2\times10^{-3}$ & $6.4\times10^{-4}$ & $0.17$ & $1.9\times10^{-3}$ & Planet \\
$201779067$ & $1$ & $1.97$ &  - & $0.036$ & $5.0\times10^{-3}$ & $0.286$ & $0.03$ & $0.327$ & Candidate \\
$201828749$ & $1$ & $0.39$ &  - & $< 10^{-4}$ & $1.7\times10^{-3}$ & $2.2\times10^{-3}$ & $0.17$ & $3.9\times10^{-3}$ & Planet \\
$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $1.7\times10^{-4}$ & Planet \\
$201912552$ & $1$ & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $6.8\times10^{-3}$ & $0.052$ & $0.05$ & $0.059$ & Candidate

>>>>

$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.21$ & $7.0\times10^{-4}$ & Planet \\
 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP\\
$201295312$ & $1$ & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet \\
$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.22$ & $1.8\times10^{-4}$ & Planet \\
$201367065$ & $1$ & $0.15$ &  - & $0.717$ & $< 10^{-4}$ & $0.044$ & $0.07$ & $0.761$ & Candidate \\
$201367065$ & $2$ & $0.67$ &  - & $3.2\times10^{-3}$ & $< 10^{-4}$ & $4.2\times10^{-3}$ & $0.17$ & $7.4\times10^{-3}$ & Planet \\
$201384232$ & $1$ & $0.44$ &  - & $1.2\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.4\times10^{-4}$ & Planet \\
$201393098$ & $1$ & $0.52$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $5.5\times10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet \\
$201403446$ & $1$ & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
$201445392$ & $1$ & $0.26$ &  - & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.012$ & $0.19$ & $0.013$ & Candidate \\
$201445392$ & $2$ & $0.18$ &  - & $0.023$ & $< 10^{-4}$ & $0.254$ & $0.21$ & $0.277$ & Candidate \\
$201465501$ & $1$ & $0.68$ &  - & $0.491$ & $0.022$ & $9.1\times10^{-3}$ & $0.20$ & $0.522$ & Candidate \\
$201505350$ & $1$ & $2.69$ &  - & $0.583$ & $< 10^{-4}$ & $0.024$ & $0.07$ & $0.607$ & Candidate \\
$201505350$ & $2$ & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Candidate \\
$201546283$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Planet \\
$201549860$ & $1$ & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate \\
$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.6\times10^{-3}$ & $0.10$ & $3.6\times10^{-3}$ & Planet \\
$201565013$ & $1$ & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate \\
 \color{red} $201569483$  & \color{red}  $1$  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.437$  & \color{red}  $0.562$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.999$  & \color{red}  FP\\
$201577035$ & $1$ & $0.14$ &  Y & $3.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $3.6\times10^{-4}$ & Planet \\
$201596316$ & $1$ & $0.45$ &  - & $0.017$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.20$ & $0.017$ & Candidate \\
$201613023$ & $1$ & $0.08$ &  Y & $9.8\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $9.8\times10^{-4}$ & Planet \\
$201617985$ & $1$ & $0.27$ &  - & $0.166$ & $< 10^{-4}$ & $0.053$ & $0.19$ & $0.219$ & Candidate \\
$201629650$ & $1$ & $0.43$ &  - & $1.5\times10^{-3}$ & $< 10^{-4}$ & $2.6\times10^{-4}$ & $0.18$ & $1.8\times10^{-3}$ & Planet \\
$201635569$ & $1$ & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.043$ & $0.06$ & $0.043$ & Candidate \\
 \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.856$  & \color{red}  $0.142$  & \color{red}  $1.6\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
$201702477$ & $1$ & $0.70$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet \\
$201736247$ & $1$ & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.6\times10^{-4}$ & $0.18$ & $4.9\times10^{-4}$ & Planet \\
$201754305$ & $1$ & $0.65$ &  - & $2.5\times10^{-3}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $5.7\times10^{-3}$ & Planet \\
$201754305$ & $2$ & $0.38$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.22$ & $3.6\times10^{-3}$ & Planet \\
 \color{red} $201779067$  & \color{red}  $1$  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP\\
$201828749$ & $1$ & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Planet \\
$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
$201912552$ & $1$ & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.8\times10^{-4}$ & $0.07$ & $2.9\times10^{-4}$ & Planet
